Cost of Living in Toronto

### 2024-09-27 paper/paper.qmd
fixed head() not displaying all the rows

#round to the nearest integer
avg_income$"Average Income in $" <- round(avg_income$"Average Income in $", 0)

avg_income %>% head() %>% knitr::kable()
```

@@

There is a huge price disparity between the expenses of the 11 families. The biggest expense was rent, at an average of $3146 per month, followed by food costs at $705. The huge cost rent highlights a need for further investigation and is discussed in @sec-discussion. See `Table 3` for an overview of the dataset.

@@

# absolute value (because employment insurance is relative to income)
avg_expense$"Average Expense in $" <- abs(avg_expense$"Average Expense in $") 
avg_expense %>% head() %>% knitr::kable()
```
## Difference between Income and Expense

>>>>

#round to the nearest integer
avg_income$"Average Income in $" <- round(avg_income$"Average Income in $", 0)
avg_income %>% head(13) %>% knitr::kable()
```

@@

There is a huge price disparity between the expenses of the 11 families. The biggest expense was rent, at an average of $3146 per month, followed by food costs at $705. The huge cost rent highlights a need for further investigation and is discussed in @sec-discussion. See `Table 3` for an overview of the dataset. Note that all the values are rounded up and therefore may not add up to the total.

@@

# absolute value (because employment insurance is relative to income)
avg_expense$"Average Expense in $" <- abs(avg_expense$"Average Expense in $")

avg_expense %>% head() %>% knitr::kable()
```
## Difference between Income and Expense
